Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State with Multivariate Techniques

### 2015-12-10 paper/sec-mva.tex
work on MVA section

In this section we study how the MVA results are modified when
signal and background events are embedded in a high-PU environment.
%
The simulation of PU and the corresponding subtraction with
{\tt SoftKiller} have been performed as described
in Sect.~\ref{sec:pileup}.
%
Following this, the cut-based analysis and the subsequent
MVA optimization have been applied using the same
settings as in the case without PU.
%
In Table~\ref{table:cutflowMVA_PU} we provide the results
  at the end of the cut-based analysis,
for the case with $\la n_{\rm PU}\ra=80$+SK.
%
It is clear that the pre-MVA 
signal significance have been seriously degraded
as compared to the case without PU.
%
We now find values for $S/\sqrt{B}$ of 0.4, 0.3 and 0.9, in the resolved,
intermediate and boosted categories, respectively, to be compared
with the corresponding values without PU, namely 1.6, 1.6 and 2.7.
%

>>>>

In this section we study how the MVA results are modified when
signal and background events are embedded in a high-PU environment.
%
The simulation of PU and the corresponding subtraction with
{\tt SoftKiller} have been performed as described
in Sect.~\ref{sec:pileup}.
%
The cut-based analysis and the subsequent
MVA optimization have been performed using exactly the same
settings as in the case without PU.
%
In Table~\ref{table:cutflowMVA_PU} we provide the results
  at the end of the cut-based analysis,
for the case with $\la n_{\rm PU}\ra=80$+SK.
%
It is clear that the pre-MVA 
signal significance has been degraded
as compared to the case without PU.
%
We now find values for $S/\sqrt{B}$ of 0.25, 0.15 and 0.31, in the resolved,
intermediate and boosted categories, respectively, to be compared
with the corresponding values without PU, namely 1.0, 0.9 and 1.0,
see Table~\ref{table:cutflowMVA}. 
%
